Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-28 README.Rmd
added more file links

- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Upload the files for submission and submit

@@

**`code`**

@@

- `01-raw-file-compression.Rmd/.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
- `02-data-preparation.Rmd/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
- `03-submission-steps.Rmd/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal

**`cover-letter`**

@@

**`data`**

@@

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
  - `CCFs_withlands.csv.zip`: raw version of the bullet training data
  - `h224-set1-features.rds.zip` and `h224-set11-features.rds.zip`: raw versions of the bullet testing data
  - `signatures.rds.zip`: raw version of the example matching signatures data
- `readme.txt` contains descriptions of the data files provided with the submission of the paper.

**`figure-static`**

@@

- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in this readme.

**`LEAscans`**

@@

**`old-version`**

@@

**`submission`**

@@

- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output.
- `references.bib` contains the bibtex information for the references in the manuscript.
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA Data Science Journal.

>>>>

- Finish documenting the identification of the training data for rtrees in research journals (including LIME explanations from different training datasets/models)
- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Upload the files for submission and submit

@@

[**`code`**](code)

@@

- [`01-raw-file-compression.Rmd`](code/01-raw-file-compression.Rmd)/`.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
- [`02-data-preparation.Rmd`](code/02-data-preparation.Rmd)`/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
- [`03-submission-steps.Rmd`](code/03-submission-steps.Rmd)`/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal

[**`cover-letter`**](cover-letter)

@@

[**`data`**](data/)

@@

- [`bullet-train.csv.zip`](data/bullet-train.csv.zip) and [`bullet-test.csv.zip`](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
  - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [`h224-set1-features.rds.zip`](data/raw/h224-set1-features.rds.zip) and [`h224-set11-features.rds.zip`](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [`signatures.rds.zip`](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [`readme.txt`](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

[**`figure-static`**](figure-static/)

@@

- [`figure-08-1.png.zip`](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
- [`figure-readme.png`](figure-static/figure-readme.png) is a figure used in this readme.

[**`LEAscans`**](LEAscans/)

@@

[**`old-version`**](old-version/)

@@

[**`submission`**](submission)

@@

- [`.gitignore`](.gitignore) contains objects to be ignored by git.
- [`paper.Rnw`](paper.Rnw), [`paper.pdf`](paper.pdf), and [`paper.tex`](paper.tex) are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- [`README.Rmd`](README.Rmd) and [`README.md`](README.md) are the readme files that generated this output.
- [`references.bib`](references.bib) contains the bibtex information for the references in the manuscript.
- [`WileyNJG-AMS.bst`](WileyNJD-AMS.bst) and [`WileyNJG-v2.cls`](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.
